### 2024-11-14 Article/Cat_of_Graphs.tex
minori
Some proofs, reordering of material
Def of subobjects, lemma 1.2.13, 1.2.15
some proofs
eqgrph pushouts reg mono van kampen
first complete
minima

\newcommand{\graph}[1]{\mathcal{#1}}
\newcommand{\Graph}{\mathbf{Graph}}
\newcommand{\EqGrph}{\mathbf{EqGrph}}
\newcommand{\Q}{Q} % Quotient functor

\chapter{Categories of Graphs}
This chapter is about graphs, and how it is possible to formalize them using categories in order to point out their properties from an abstract point of view. Starting from the set-theoretical definition of graphs, we will give an abstraction via functor categories, in which a graph is nothing but a functor between a category to another.

\input{Graph_sections/Graphs}
\input{Graph_sections/Eq_Graphs}
\input{Graph_sections/EGGs}

>>>>

\renewcommand{\graph}[1]{\mathcal{#1}}
\newcommand{\Graph}{\mathbf{Graph}}
\newcommand{\EqGrph}{\mathbf{EqGrph}}
\newcommand{\Q}{Q} % Quotient functor

\chapter{Categories of Graphs}
This chapter is about graphs, and how it is possible to formalize them using categories in order to point out their properties from an abstract point of view. Starting from the set-theoretical definition of graphs, we will give an abstraction via functor categories, in which a graph is nothing but a functor between categories.

\input{Graph_sections/Graphs}
%\input{Graph_sections/Eq_Graphs_Notes_Results}
\input{Graph_sections/Eq_Graphs_integration}
\input{Graph_sections/EGGs}

### 2024-11-14 Article/Graph_sections/Eq_Graphs_integration.tex
minima

Another functor that will be useful later is $V: \EqGrph \to \Set$, that sends $(E_G, V_G, C_G, s_G, t_G, q_G)$ to $C_G$, and $h = (h_E, h_V, h_C)$ to $h_C$.

@@

	For $C'_1$, we can make a similar argument, let $S$ be the pullback of $m_2$ along $x_1$, using \Cref{lemma:pullback_lemma} and, again, the proof of \Cref{prop:eqgrph_complete} we know that $q'_1$ arise as the factorization of the arrow $B'_1\to S$ induced by $q'_2\circ h'_2$ and $a_2$ so that we have a diagram.
	\[\begin{tikzcd}[row sep = 20, column sep =20]
	{B'_1} && {B'_2} \\
	\\
	{C'_3} && S && {C'_2} \\
	\\
	{B_1} && T && U \\
	\\
	&& {C_1} && {C_2}
	\arrow["{h'_V}", from=1-1, to=1-3]
	\arrow["{q'_1}", from=1-1, to=3-1]
	\arrow["{q'_2}", from=1-3, to=3-5, bend left = 20]
	\arrow["{m_1}", from=3-1, to=3-3]
	\arrow["{s_1}", from=3-3, to=3-5]
	\arrow["{s_2}"', from=3-3, to=5-3]
	\arrow["{m_2}", from=3-5, to=5-5]
	\arrow["{q_1}"', from=5-1, to=7-3, bend right = 20, shift right = 1]
	\arrow["{x_1}", from=5-3, to=5-5]
	\arrow["{x_2}"', from=5-3, to=7-3]
	\arrow["{u_2}", from=5-5, to=7-5]
	\arrow["{h_C}"', from=7-3, to=7-5]
        \arrow["{a_V}"', from=1-1, to=5-1, bend right = 20, shift right = 1]
	\end{tikzcd}\]

	Moreover, we have that
	\[
		\begin{split}
			s_1 \circ m_1 \circ q_1 &= q'2 \circ h'_V \\ &= h'_C \circ q'_1
		\end{split}\qquad\begin{split}
			q'_4 \circ t'_V &= t'_C \circ q'_2\\ &= u_1\circ m_2 \circ q'_2
		\end{split}\quad\begin{split}
			y_1 \circ m_3 \circ q'_3 &= p'_V \circ q'_4\\ &= p'_C \circ q'_3
		\end{split}\qquad\begin{split}TODO:\ w \circ s_2 \circ m_1 = m_3 \circ k_C'
		\end{split}
	\]
	Hence, $s_1\circ m_1 = h'_C$, $w \circ s_2 \circ m_1 = m_3 \circ k_C'$, $t'_C = u_1 \circ m_2$ and $p_C = y_1 \circ m_3$.
	Let now $z: \graph{G}'_2 \to \graph H = (E, V, Q, s, t, q)$, $w: \graph G_3^1 \to \graph H$ be two morphisms such that $z \circ h' = w \circ k'$, and let $\phi:B'_4 \to V$ be the arrow induced by $z_V$ and $w_V$. We want to construct the arrow $v: C'_4 \to Q$ in the diagram below.
	\[\begin{tikzcd}[row sep = 25, column sep = 25]
	& {B_1'} && {B_2'} \\
	{B_3'} && {B_4'} && V \\
	& T && U \\
	Y && {C_4'} && Q \\
	& {C_1} && {C_2} \\
	{C_3} && {C_4}
	\arrow["{h_V'}", from=1-2, to=1-4]
	\arrow["{k_V'}"', from=1-2, to=2-1]
	\arrow["{s_2\circ m_1 \circ q_1'}"{description, pos=0.7}, from=1-2, to=3-2]
	\arrow["{t_V'}", from=1-4, to=2-3]
	\arrow["{z_V}", from=1-4, to=2-5]
	\arrow["{m_2\circ q'_2}"{pos=0.7}, from=1-4, to=3-4]
	\arrow["{m_3 \circ q'_3}"', from=2-1, to=4-1]
	\arrow["q", from=2-5, to=4-5]
	\arrow["{x_1}"{pos=0.8}, from=3-2, to=3-4]
	\arrow["w"', from=3-2, to=4-1]
	\arrow["{x_2}"'{pos=0.7}, from=3-2, to=5-2]
	\arrow["{u_1}", from=3-4, to=4-3]
	\arrow["{u_2}"{pos=0.7}, from=3-4, to=5-4]
	\arrow["{y_2}"', from=4-1, to=6-1]
	\arrow["{h_C}"{pos=0.8}, from=5-2, to=5-4]
	\arrow["{k_C}", from=5-2, to=6-1]
	\arrow["{t_C}", from=5-4, to=6-3]
	\arrow["{p_C}"', from=6-1, to=6-3]
	\arrow["{p_V'}"{pos=0.8}, from=2-1, to=2-3, crossing over]
	\arrow["\phi"{pos=0.8}, from=2-3, to=2-5, crossing over]
	\arrow["{q'_4}"'{pos=0.7}, from=2-3, to=4-3, crossing over]
	\arrow["{y_1}"{pos=0.7}, from=4-1, to=4-3, crossing over]
	\arrow["{d_C}"'{pos=0.7}, from=4-3, to=6-3, crossing over]
	\arrow["v"{pos=0.8}, dashed, from=4-3, to=4-5, crossing over]
	\end{tikzcd}\]

>>>>

Another functor that will be useful later is $V: \EqGrph \to \Set$, sending $(E_G, V_G, C_G, s_G, t_G, q_G)$ to $C_G$ and $h = (h_E, h_V, h_C)$ to $h_C$.

@@

	For $C'_1$, we can make a similar argument, let $S$ be the pullback of $m_2$ along $x_1$, using \Cref{lemma:pullback_lemma} and, again, the proof of \Cref{prop:eqgrph_complete} we know that $q'_1$ arise as the factorization of the arrow $B'_1\to S$ induced by $q'_2\circ h'_2$ and $a_2$ so that we have a diagram.
	\[\begin{tikzcd}[row sep = 20, column sep =20]
	{B'_1} && {B'_2} \\
	\\
	{C'_1} && S && {C'_2} \\
	\\
	{B_1} && T && U \\
	\\
	&& {C_1} && {C_2}
	\arrow["{h'_V}", from=1-1, to=1-3]
	\arrow["{q'_1}", from=1-1, to=3-1]
	\arrow["{q'_2}", from=1-3, to=3-5, bend left = 20]
	\arrow["{m_1}", from=3-1, to=3-3]
	\arrow["{s_1}", from=3-3, to=3-5]
	\arrow["{s_2}"', from=3-3, to=5-3]
	\arrow["{m_2}", from=3-5, to=5-5]
	\arrow["{q_1}"', from=5-1, to=7-3, bend right = 20, shift right = 1]
	\arrow["{x_1}", from=5-3, to=5-5]
	\arrow["{x_2}"', from=5-3, to=7-3]
	\arrow["{u_2}", from=5-5, to=7-5]
	\arrow["{h_C}"', from=7-3, to=7-5]
        \arrow["{a_V}"', from=1-1, to=5-1, bend right = 20, shift right = 1]
	\end{tikzcd}\]

	Moreover, we have that
	\[
		\begin{split}
			s_1 \circ m_1 \circ q_1 &= q'_2 \circ h'_V \\ &= h'_C \circ q'_1
		\end{split}\qquad\begin{split}
			q'_4 \circ t'_V &= t'_C \circ q'_2\\ &= u_1\circ m_2 \circ q'_2
		\end{split}
	\]\[
		\begin{split}
			y_1 \circ m_3 \circ q'_3 &= p'_V \circ q'_4\\ &= p'_C \circ q'_3
		\end{split}\qquad\begin{split}TODO:\ w \circ s_2 \circ m_1 = m_3 \circ k_C'
		\end{split}
	\]
	Hence, $s_1\circ m_1 = h'_C$, $w \circ s_2 \circ m_1 = m_3 \circ k_C'$, $t'_C = u_1 \circ m_2$ and $p'_C = y_1 \circ m_3$.
	Let now $z: \graph{G}'_2 \to \graph H = (E, V, Q, s, t, q)$, $w: \graph G_3^1 \to \graph H$ be two morphisms such that $z \circ h' = w \circ k'$, and let $\phi:B'_4 \to V$ be the arrow induced by $z_V$ and $w_V$. We want to construct the arrow $v: C'_4 \to Q$ in the diagram below.
	\[\begin{tikzcd}[row sep = 25, column sep = 25]
	& {B_1'} && {B_2'} \\
	{B_3'} && {B_4'} && V \\
	& T && U \\
	Y && {C_4'} && Q \\
	& {C_1} && {C_2} \\
	{C_3} && {C_4}
	\arrow["{h_V'}", from=1-2, to=1-4]
	\arrow["{k_V'}"', from=1-2, to=2-1]
	\arrow["{s_2\circ m_1 \circ q_1'}"{description, pos=0.7}, from=1-2, to=3-2]
	\arrow["{t_V'}", from=1-4, to=2-3]
	\arrow["{z_V}", from=1-4, to=2-5]
	\arrow["{m_2\circ q'_2}"{pos=0.7}, from=1-4, to=3-4]
	\arrow["{m_3 \circ q'_3}"', from=2-1, to=4-1]
	\arrow["q", from=2-5, to=4-5]
	\arrow["{x_1}"{pos=0.8}, from=3-2, to=3-4]
	\arrow["w"', from=3-2, to=4-1]
	\arrow["{x_2}"'{pos=0.7}, from=3-2, to=5-2]
	\arrow["{u_1}", from=3-4, to=4-3]
	\arrow["{u_2}"{pos=0.7}, from=3-4, to=5-4]
	\arrow["{y_2}"', from=4-1, to=6-1]
	\arrow["{h_C}"{pos=0.8}, from=5-2, to=5-4]
	\arrow["{k_C}", from=5-2, to=6-1]
	\arrow["{t_C}", from=5-4, to=6-3]
	\arrow["{p_C}"', from=6-1, to=6-3]
	\arrow["{p_V'}"{pos=0.8}, from=2-1, to=2-3, crossing over]
	\arrow["\phi"{pos=0.8}, from=2-3, to=2-5, crossing over]
	\arrow["{q'_4}"'{pos=0.7}, from=2-3, to=4-3, crossing over]
	\arrow["{y_1}"{pos=0.7}, from=4-1, to=4-3, crossing over]
	\arrow["{d_C}"'{pos=0.7}, from=4-3, to=6-3, crossing over]
	\arrow["v"{pos=0.8}, dashed, from=4-3, to=4-5, crossing over]
	\end{tikzcd}\]

### 2024-11-14 Article/Graph_sections/Graphs.tex
minima

A (directed graph) $\graph{G}$ is a mathematical structure consisting of a set of edge, a set of nodes and two functions, one assigning a \emph{source} node and one assigning a \emph{target} node to an edge. Formally, $\graph{G}$ is a quadruple $(V_\graph{G}, E_\graph{G}, s_\graph{G}, t_\graph{G})$, where $V_\graph{G}$ is the set of nodes, $E_\graph{G}$ is the set of edges, and $s_\graph{G}, t_\graph{G}: E_\graph{G} \rightarrow V_\graph{G}$ are the source and the target functions.

>>>>

A (directed graph) $\graph{G}$ is a structure consisting of a set of edge, a set of nodes and two functions, one assigning a \emph{source} node and one assigning a \emph{target} node to an edge. Formally, $\graph{G}$ is a quadruple $(V_\graph{G}, E_\graph{G}, s_\graph{G}, t_\graph{G})$, where $V_\graph{G}$ is the set of nodes, $E_\graph{G}$ is the set of edges, and $s_\graph{G}, t_\graph{G}: E_\graph{G} \rightarrow V_\graph{G}$ are the source and the target functions.
